\begin{thebibliography}{999}

%
% Chapter 1
%

\bibitem{A Break in the Clouds: Towards a Cloud Definition}
http://doi.acm.org/10.1145/1496091.1496100
Vaquero, Luis M. and Rodero-Merino, Luis and Caceres, Juan and Lindner, Maik. A Break in the Clouds: Towards a Cloud Definition. ACM, 2009.

\bibitem{Developing Software Online With Platform-as-a-Service Technology}
Lawton, G. Developing Software Online With Platform-as-a-Service Technology. 2008

\bibitem{A survey and taxonomy of infrastructure as a service and web hosting cloud providers}
Prodan, R. and Ostermann, S. A survey and taxonomy of infrastructure as a service and web hosting cloud providers, Grid Computing, 2009 10th IEEE/ACM International Conference on

\bibitem{Understanding service-oriented software}
Gold, N. and Mohan, A. and Knight, C. and Munro, M.  Understanding service-oriented software. IEEE, 2004

%
% Chapter 2
%

\bibitem{PetsVsCattle}
https://blog.engineyard.com/2014/pets-vs-cattle
Noah Slater. Pets vs. Cattle. Engine Yard, 2014.

\bibitem{DoOperatingSystemsStillMatter}
http://ianmurdock.com/cloud/do-operating-systems-still-matter/
Ian Murdock. Do operating systems still matter? Ian Murdock, 2009.

\bibitem{ThePlatformAbstractionAdvantageOfPaaS}
https://blog.openshift.com/platform-abstraction-advantage/
Krishnan Subramanian. The Platform Abstraction Advantage of PaaS. Red Hat, 2015.

\bibitem{TheTwelveFactors}
http://12factor.net/
The Twelve-Factor App. Heroku, 2012.

\bibitem{ContinuousDelivery}
http://ptgmedia.pearsoncmg.com/images/9780321601919/samplepages/0321601912.pdf
Humble, Jez, and David Farley. Continuous delivery: reliable software releases through build, test, and deployment automation. Pearson Education, 2010.

\bibitem{Docker: Lightweight Linux Containers for Consistent Development and Deployment}
http://dl.acm.org/citation.cfm?id=2600239.2600241
Merkel, Dirk. Docker: Lightweight Linux Containers for Consistent Development and Deployment. Belltown Media, 2014.

\bibitem{Adopting DevOps Practices in Quality Assurance}
http://doi.acm.org/10.1145/2524713.2524721
Roche, James. Adopting DevOps Practices in Quality Assurance. ACM, 2013.

% \item http://microservices.io/articles/scalecube.html
% \item http://martinfowler.com/articles/microservices.html

\bibitem{FreeSoftwareDefinition}
https://www.gnu.org/philosophy/free-sw.html
FSF Contributors. Free Software Foundation, 2015.

%
% Chapter 3
%

\bibitem{OpenContainerProject}
https://www.opencontainers.org/pressrelease/
Industry Leaders Unite to Create Project for Open Container Standards. Linux Foundation, 2015.

%
% Chapter 4
%

\bibitem{CloudNativeComputingFoundation}
http://www.linuxfoundation.org/news-media/announcements/2015/07/new-cloud-native-computing-foundation-drive-alignment-among/
New Cloud Native Computing Foundation to Drive Alignment Among Container Technologies. Linux Foundation, 2015.

%
% Chapter 5
%

%
% Chapter 6
%


%
% Chapter 7
%

\bibitem{HighAvailability}
http://doi.acm.org/10.1145/227210.227227
Dolev, Danny and Malki, Dalia. The Transis Approach to High Availability Cluster Communication. ACM, 1996

\end{thebibliography}